Merging merges, more or less

### 2015-03-20 2015mergingmerges/section/02-Machines.tex
ok

>>>>

To perform this invariant checking, we annotate each state with a set of available information at that state.
The available information can be that there exists some value that can be used, or that a channel is finished or closed.
For invariant checking, we do not distinguish between finished and closed channels.

\begin{tabbing}
MM \= M \= \kill
$\Psi$ \> $=$  \> $@Value@~n$ \\
       \> $~|$ \> $@Finished@~n$ \\
\end{tabbing}

To begin, we annotate the initial state with an empty set of information: at the start of the machine, we have no read values available, nor is it known (or likely!) that any channels are finished.
Then, for each output transition, we annotate the output state according to the current state type and the transition label: @Pull n@ adds a @Value n@ or @Finished n@ to its @Some n@ and @None@ transitions.
If the output state has already been annotated, we check that the two annotations are the same, modulo values produced by @Out@.
The reason that annotations may be different in the values produced by @Out@ is that the @Out@ values are not explicitly released, and may be referred to by other functions, for example after fusing two combinators together.

\input{figures/Invariants.tex}

\begin{tabbing}
MMMMMM \= M \= MMMMMMMMM \= M \= \kill

$@out@(s, t, a)$
 \> $~|$ \> $s = @Pull@~n $ \> $ \wedge$ \> $t = @Some@~n$ \\
 \> $=$  \> $ a \cup \{@Value@~n\} $ \\
\\
 \> $~|$ \> $s = @Pull@~n $ \> $ \wedge$ \> $t = @None@$ \\
 \> $=$  \> $ a \cup \{@Finished@~n\} $ \\
\\
 \> $~|$ \> $s = @Release@~n $ \\
 \> $=$  \> $ a \setminus \{@Value@~n\} $ \\
\\
 \> $~|$ \> $s = @Close@~n $ \\
 \> $=$  \> $ a \cup \{@Finished@~n\} $ \\
\\
 \> $~|$ \> $s = @Update@~f~n $ \\
 \> $=$  \> $ a $ \\
\\
 \> $~|$ \> $s = @If@~f~n $ \\
 \> $=$  \> $ a $ \\
\\
 \> $~|$ \> $s = @Out@~f~n $ \\
 \> $=$  \> $ a \cup \{@Value@~n\} $ \\
\\
 \> $~|$ \> $s = @OutFinished@~n $ \\
 \> $=$  \> $ a \cup \{@Finished@~n\} $ \\
\\
 \> $~|$ \> $s = @Skip@ $ \\
 \> $=$  \> $ a $ \\
\end{tabbing}

After each state is annotated, we check that its annotation allows the state type 
For each state, we also check that its annotation allows its execution: a @Pull n@ cannot run if $n$ is already finished; @Release n@ can only run if there is a @Value n@ to release, and so on.

\begin{tabbing}
MMMMMM \= M \= \kill

$@check@(s, a)$
 \> $~|$ \> $s = @Pull@~n$ \\
 \> $=$  \> $ @Value@~n \not\in a \wedge @Finished@~n \not\in a $ \\
\\
 \> $~|$ \> $s = @Release@~n$ \\
 \> $=$  \> $ @Value@~n \in a$ \\
\\
 \>      \> $\cdots$
\end{tabbing}

### 2015-03-20 2015mergingmerges/section/03-Access.tex
ok

If the first machine is producing an output on channel $n$ and the second machine uses $n$, the first machine would usually have to wait until the second machine is ready to accept new data.
However, if the second machine is @Done@, the first machine may output to the channel as frequently as it likes.
Note that the output channel $n$ may have multiple consumers, so continuing to output after the second machine consumer has finished is not as futile as it may seem at first.
\TODO{Although, all the combinators so far use the whole input, and anyway checking for @Done@ of machine is too fine-grained if machine already has multiple combinators; perhaps an ``I promise not to read from X any more'' state would be interesting.}

>>>>

If the first machine is producing an output on channel $n$ and the second machine uses $n$, the first machine would usually have to wait until the second machine is ready to accept new data.
However, if the second machine is @Done@, the first machine may output to the channel as frequently as it likes.
Note that the output channel $n$ may have multiple consumers, so continuing to output after the second machine consumer has finished is not as futile as it may seem at first.
\TODO{Checking for @Done@ of machine is too coarse-grained, need to check if $n$ is closed instead.}
